An Example Article

### 2023-04-26 article-en/article-temp-header.tex
update

\documentclass[10pt,reqno,final]{article}
%\documentclass[10pt,reqno,draft]{article}

@@

@@

%\fancyhead[CO]{\uppercase{Title of Paper}}
%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
%\fancyhead[RO]{\thepage}
%\fancyhead[LE]{\thepage}

@@

% caption setting
%\captionsetup{font={small,singlespacing},labelfont={bf},labelformat={default},labelsep=period}
\captionsetup{font={small},labelformat={default},labelsep=period}
\captionsetup[figure]{position=bottom,skip={5pt},name={Figure}}
\captionsetup[table]{position=top,skip={2pt},name={Table}}
%\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
%\setlength{\floatsep}{10pt plus 2pt minus 2pt}
%\setlength{\intextsep}{10pt plus 2pt minus 2pt}
%\setlength{\abovecaptionskip}{2pt plus 1pt minus 1pt}
%\setlength{\belowcaptionskip}{3pt plus 1pt minus 2pt}

@@

% redefine abstract environment
\makeatletter
\renewenvironment{abstract}{%
    \if@twocolumn
      \section*{\abstractname}%
    \else %% <- here removed \small
      \begin{center}%
        {\bfseries \large\abstractname\vspace{\z@}} %% <- here added \large
      \end{center}%
      \quotation
    \fi}
    {\if@twocolumn\else\endquotation\fi}
\makeatother

@@

\author[1]{Author A\thanks{Email address: \texttt{A.A@university.edu}; Corresponding author.}}
\author[1]{Author B\thanks{Email address: \texttt{B.B@university.edu}}}
\author[2]{Author C\thanks{Email address: \texttt{C.C@university.edu}}}
%\author[2]{Author D\thanks{Email address: \texttt{D.D@university.edu}}}
\affil[1]{Department of Mathematics, \LaTeX\ University.}
\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}

>>>>

\documentclass[10pt,twoside,reqno,final]{article}
%\documentclass[10pt,reqno,draft]{article}

@@

\makeatletter
\newcommand\@shorttitle{}
\newcommand\shorttitle[1]{\def\@shorttitle{#1}}
\newcommand\@shortauthor{}
\newcommand\shortauthor[1]{\def\@shortauthor{#1}}
\makeatother

@@

\makeatletter
\pagestyle{fancy}
\fancyhf{}
\fancyhead[CO]{\@shorttitle}
\fancyhead[CE]{\@shortauthor}
\fancyhead[RO]{\thepage}
\fancyhead[LE]{\thepage}
\makeatother

@@

% caption setting
%\captionsetup{font={small,singlespacing},labelfont={bf},labelformat={default},labelsep=period}
\captionsetup{labelformat={default},labelsep=period}
\captionsetup[figure]{position=bottom,skip={8pt},name={Figure}}
\captionsetup[table]{position=top,skip={4pt},name={Table}}
%\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
%\setlength{\floatsep}{10pt plus 2pt minus 2pt}
%\setlength{\intextsep}{10pt plus 2pt minus 2pt}
%\setlength{\abovecaptionskip}{2pt plus 1pt minus 1pt}
%\setlength{\belowcaptionskip}{3pt plus 1pt minus 2pt}

@@

% redefine maketitle environment
\makeatletter
\def\@maketitle{%
  \newpage
  \null
  %\vspace{-1.5em}%
  \begin{center}%
    \let \footnote \thanks
    {\Large \bfseries \@title \par}%
    \vskip 1.5em%
    {\large
      \lineskip 0.5em%
      \begin{tabular}[t]{c}%
        \@author
      \end{tabular}\par}%
    \vskip 0.5em%
    {\large \@date}%
  \end{center}%
  \par
  \vskip 1em
}
\makeatother

% redefine abstract environment
\makeatletter
\renewenvironment{abstract}{%
  \if@twocolumn
    \section*{\abstractname}%
  \else %% <- here removed \small
    \begin{center}%
      {\bfseries \large\abstractname\vspace{\z@}} %% <- here added \large
    \end{center}%
    \quotation
  \fi}{
  \if@twocolumn\else\endquotation\fi
}
\makeatother

@@

\shorttitle{Short Title of Article}
\shortauthor{Author A, Author B, and Author C}

\author[1]{Author A\thanks{Email address: \texttt{A.A@university.edu}; Corresponding author.}}
\author[1]{Author B\thanks{Email address: \texttt{B.B@university.edu}}}
\author[2]{Author C\thanks{Email address: \texttt{C.C@university.edu}}}
%\author[2]{Author D\thanks{Email address: \texttt{D.D@university.edu}}}
\affil[1]{Department of Mathematics, \LaTeX\ University}
\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}

### 2023-04-26 article-en/article-temp2.tex
update

% package for mathematics
\usepackage{amsmath,amssymb,amsthm}
% package for RSFS fonts in maths
\usepackage{mathrsfs}
% package for special symbols
\usepackage{pifont}
% package for multilingual support
\usepackage[english]{babel}
% package for figures
\usepackage{graphicx}
\usepackage{subfigure}
% package for hyperlink
\usepackage{hyperref}
% package for layout of list
\usepackage{enumitem}
% package for showing keys in draft mode
\usepackage[notcite,notref]{showkeys}
% package for color
\usepackage{color}
% package for table
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{makecell}
% package for multiple columns and rows
\usepackage{multirow,multicol}
% package for caption
\usepackage{caption}
% package for algorithm
\usepackage{algorithm,algorithmicx}
\usepackage{algpseudocode}
% package for author and affiliation style
\usepackage[affil-it]{authblk}
% package for using box and verbatim
\usepackage{fancybox}
% package for page headers and footers
\usepackage{fancyhdr}

% package for section etc.
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{\thesection.}{1.2ex}{}
\titleformat{\subsection}{\normalfont\bfseries}{\thesubsection.}{1.2ex}{}
\titleformat{\subsubsection}{\normalfont\slshape}{\thesubsubsection.}{1.2ex}{}

@@

% headers and footers setting
%\pagestyle{fancy}
%\fancyhf{}
%\fancyhead[CO]{\uppercase{Title of Paper}}
%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
%\fancyfoot[C]{\thepage}
%\renewcommand{\headrulewidth}{0pt}

%\fancyhead[C]{\uppercase{Title of Paper}}
%\fancyfoot[C]{\thepage}
%\renewcommand{\headrulewidth}{0pt}

%\fancyhead[CO]{\uppercase{Title of Paper}}
%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
%\fancyhead[RO]{\thepage}
%\fancyhead[LE]{\thepage}

@@

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% caption setting
%\captionsetup{font={small,singlespacing},labelfont={bf},labelformat={default},labelsep=period}
\captionsetup{font={small},labelformat={default},labelsep=period}
\captionsetup[figure]{position=bottom,skip={5pt},name={Figure}}
\captionsetup[table]{position=top,skip={2pt},name={Table}}
%\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
%\setlength{\floatsep}{10pt plus 2pt minus 2pt}
%\setlength{\intextsep}{10pt plus 2pt minus 2pt}
%\setlength{\abovecaptionskip}{2pt plus 1pt minus 1pt}
%\setlength{\belowcaptionskip}{3pt plus 1pt minus 2pt}

@@

% redefine abstract environment
\makeatletter
\renewenvironment{abstract}{%
    \if@twocolumn
      \section*{\abstractname}%
    \else %% <- here removed \small
      \begin{center}%
        {\bfseries \large\abstractname\vspace{\z@}} %% <- here added \large
      \end{center}%
      \quotation
    \fi}
    {\if@twocolumn\else\endquotation\fi}
\makeatother

@@

\author[1]{Author A\thanks{Email address: \texttt{A.A@university.edu}; Corresponding author.}}
\author[1]{Author B\thanks{Email address: \texttt{B.B@university.edu}}}
\author[2]{Author C\thanks{Email address: \texttt{C.C@university.edu}}}
%\author[2]{Author D\thanks{Email address: \texttt{D.D@university.edu}}}
\affil[1]{Department of Mathematics, \LaTeX\ University.}
\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}

\date{Date: \today}

@@

LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation.
LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents.

>>>>

% package for mathematics
\usepackage{amsmath,amssymb,amsthm}
% package for RSFS fonts in maths
\usepackage{mathrsfs}
% package for special symbols
\usepackage{pifont}
% package for multilingual support
\usepackage[english]{babel}
% package for figures
\usepackage{graphicx}
\usepackage{subfigure}
% package for hyperlink
\usepackage{hyperref}
% package for layout of list
\usepackage{enumitem}
% package for showing keys in draft mode
\usepackage[notcite,notref]{showkeys}
% package for color
\usepackage{color}
% package for table
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{makecell}
% package for multiple columns and rows
\usepackage{multirow,multicol}
% package for caption
\usepackage{caption}
% package for algorithm
\usepackage{algorithm,algorithmicx}
\usepackage{algpseudocode}
% package for using box and verbatim
\usepackage{fancybox}

@@

@@

\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]

% caption setting
%\captionsetup{font={small,singlespacing},labelformat={default},labelsep=period}
\captionsetup[figure]{position=bottom,skip={8pt},name={Figure}}
\captionsetup[table]{position=top,skip={4pt},name={Table}}
%\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
%\setlength{\floatsep}{10pt plus 2pt minus 2pt}
%\setlength{\intextsep}{10pt plus 2pt minus 2pt}
%\setlength{\abovecaptionskip}{2pt plus 1pt minus 1pt}
%\setlength{\belowcaptionskip}{3pt plus 1pt minus 2pt}

@@

@@

%\author{Author A, Author B, and J. E. Smith\thanks{Corresponding author (\textit{E-mail address:} \texttt{xyz@math.univ.edu}).} }

\author{
  Author A \\
  {\itshape Department of Computer Science, \LaTeX\ University} \\
  \and
  Author B\thanks{Email address: \texttt{xyz@math.univ.edu}} \\
  {\itshape Department of Mathematics, \LaTeX\ University} \\
  \and
  Author C\thanks{This author was supported in part by NSF Grant No. 12345678.} \\
  {\itshape Department of Mechanical Engineering, \LaTeX\ University} \\
}

\date{\today}

@@

%LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation.
%LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents.

### 2023-04-26 article-en/article-temp3.tex
update

% package for mathematics
\usepackage{amsmath,amssymb,amsthm}
% package for RSFS fonts in maths
\usepackage{mathrsfs}
% package for special symbols
\usepackage{pifont}
% package for multilingual support
\usepackage[english]{babel}
% package for figures
\usepackage{graphicx}
\usepackage{subfigure}
% package for hyperlink
\usepackage{hyperref}
% package for layout of list
\usepackage{enumitem}
% package for showing keys in draft mode
\usepackage[notcite,notref]{showkeys}
% package for color
\usepackage{color}
% package for table
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{makecell}
% package for multiple columns and rows
\usepackage{multirow,multicol}
% package for caption
\usepackage{caption}
% package for algorithm
\usepackage{algorithm,algorithmicx}
\usepackage{algpseudocode}
% package for using box and verbatim
\usepackage{fancybox}

@@

@@

\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]

% caption setting
%\captionsetup{font={small,singlespacing},labelformat={default},labelsep=period}
\captionsetup[figure]{position=bottom,skip={5pt},name={Figure}}
\captionsetup[table]{position=top,skip={2pt},name={Table}}
%\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
%\setlength{\floatsep}{10pt plus 2pt minus 2pt}
%\setlength{\intextsep}{10pt plus 2pt minus 2pt}
%\setlength{\abovecaptionskip}{2pt plus 1pt minus 1pt}
%\setlength{\belowcaptionskip}{3pt plus 1pt minus 2pt}

@@

@@

%\author{Author A, Author B, and J. E. Smith\thanks{Corresponding author (\textit{E-mail address:} \texttt{xyz@math.univ.edu}).} }

\author{
  Author A \\
  {\itshape Department of Computer Science, \LaTeX\ University} \\
  \and
  Author B\thanks{Email address: \texttt{xyz@math.univ.edu}} \\
  {\itshape Department of Mathematics, \LaTeX\ University} \\
  \and
  Author C\thanks{This author was supported in part by NSF Grant No. 12345678.} \\
  {\itshape Department of Mechanical Engineering, \LaTeX\ University} \\
}

\date{\today}

@@

The merits of our method are as follows:
\begin{itemize}
  \item item one
  \item item two
  %\item item three
\end{itemize}
\begin{enumerate}
  \item item one
  \item item two
  %\item item three
\end{enumerate}

@@

%LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation.
%LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents.

>>>>

% package for mathematics
\usepackage{amsmath,amssymb,amsthm}
% package for RSFS fonts in maths
\usepackage{mathrsfs}
% package for special symbols
\usepackage{pifont}
% package for multilingual support
\usepackage[english]{babel}
% package for figures
\usepackage{graphicx}
\usepackage{subfigure}
% package for hyperlink
\usepackage{hyperref}
% package for layout of list
\usepackage{enumitem}
% package for showing keys in draft mode
\usepackage[notcite,notref]{showkeys}
% package for color
\usepackage{color}
% package for table
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{makecell}
% package for multiple columns and rows
\usepackage{multirow,multicol}
% package for caption
\usepackage{caption}
% package for algorithm
\usepackage{algorithm,algorithmicx}
\usepackage{algpseudocode}
% package for author and affiliation style
\usepackage[affil-it]{authblk}
% package for using box and verbatim
\usepackage{fancybox}
% package for page headers and footers
\usepackage{fancyhdr}

% package for section etc.
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{\thesection.}{1.2ex}{}
\titleformat{\subsection}{\normalfont\bfseries}{\thesubsection.}{1.2ex}{}
\titleformat{\subsubsection}{\normalfont\slshape}{\thesubsubsection.}{1.2ex}{}

@@

% headers and footers setting
%\pagestyle{fancy}
%\fancyhf{}
%\fancyhead[CO]{\uppercase{Title of Paper}}
%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
%\fancyfoot[C]{\thepage}
%\renewcommand{\headrulewidth}{0pt}

%\fancyhead[C]{\uppercase{Title of Paper}}
%\fancyfoot[C]{\thepage}
%\renewcommand{\headrulewidth}{0pt}

%\fancyhead[CO]{\uppercase{Title of Paper}}
%\fancyhead[CE]{\uppercase{Author A, Author B \& Author C}}
%\fancyhead[RO]{\thepage}
%\fancyhead[LE]{\thepage}

@@

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% caption setting
%\captionsetup{font={small,singlespacing},labelfont={bf},labelformat={default},labelsep=period}
\captionsetup{labelformat={default},labelsep=period}
\captionsetup[figure]{position=bottom,skip={8pt},name={Figure}}
\captionsetup[table]{position=top,skip={4pt},name={Table}}
%\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}
%\setlength{\floatsep}{10pt plus 2pt minus 2pt}
%\setlength{\intextsep}{10pt plus 2pt minus 2pt}
%\setlength{\abovecaptionskip}{2pt plus 1pt minus 1pt}
%\setlength{\belowcaptionskip}{3pt plus 1pt minus 2pt}

@@

% redefine maketitle environment
\makeatletter
\def\@maketitle{%
  \newpage
  \null
  %\vspace{-1.5em}%
  \begin{center}%
    \let \footnote \thanks
    {\Large \bfseries \@title \par}%
    \vskip 1.5em%
    {\large
      \lineskip 0.5em%
      \begin{tabular}[t]{c}%
        \@author
      \end{tabular}\par}%
    \vskip 0.5em%
    {\large \@date}%
  \end{center}%
  \par
  \vskip 1em
}
\makeatother

% redefine abstract environment
\makeatletter
\renewenvironment{abstract}{%
  \if@twocolumn
    \section*{\abstractname}%
  \else %% <- here removed \small
    \begin{center}%
      {\bfseries \large\abstractname\vspace{\z@}} %% <- here added \large
    \end{center}%
    \quotation
  \fi}{
  \if@twocolumn\else\endquotation\fi
}
\makeatother

@@

\author[1]{Author A\thanks{Email address: \texttt{A.A@university.edu}; Corresponding author.}}
\author[1]{Author B\thanks{Email address: \texttt{B.B@university.edu}}}
\author[2]{Author C\thanks{Email address: \texttt{C.C@university.edu}}}
%\author[2]{Author D\thanks{Email address: \texttt{D.D@university.edu}}}
\affil[1]{Department of Mathematics, \LaTeX\ University}
\affil[2]{Department of Mechanical Engineering, \LaTeX\ University}

\date{Date: \today}

@@

The merits of our method are as follows:
\begin{itemize}
  \item item one
  \item item two
\end{itemize}
\begin{enumerate}
  \item item one
  \item item two
\end{enumerate}

@@

LaTeX is a high-quality typesetting system; it includes features designed for the production of technical and scientific documentation.
LaTeX is based on the idea that it is better to leave document design to document designers, and to let authors get on with writing documents.
